HGP analysis

### 2019-03-01 rick/1KGP.Rmd
update

loci <- c(1,4,5)
names(loci) <- loci

data_list <- map(loci, 
                 to_datalist,
                 data_genotype=chr20_mtx,
                 data_iaf=chr20sub_ial)

@@

```{r}
avg_qual_mean <- bas_dt$avg_qual_mean
data_list <- 
  data_list %>%
  mutate(
    fit = future_map(dataset,~ glm(genotype ~ avg_qual_mean + offset(iaf), family ="binomial", data=.x)),
    tidied = future_map(fit, tidy),
    glanced = future_map(fit, glance)
)
```

get all p-values
```{r}
p_values_dt <-
  data_list  %>% 
  select(tidied) %>% 
  map_depth( 2, "p.value") %>% 
  map_depth( 2, c(2)) %>% # c(1) for the intercept
  unlist(use.names = FALSE) %>% 
  enframe(name = "locus" ,
          value= "p.value")%>%
  mutate(locus= data_list$locus)

p_values_dt
```
get a p-value for target specific loci

>>>>

loci <- c(1:1000)
names(loci) <- loci

data_list <- future_map(loci, 
                 to_datalist,
                 data_genotype=chr20_mtx,
                 data_iaf=chr20sub_ial)

@@

```{r}
avg_qual_mean <- bas_dt$avg_qual_mean

data_list <- 
  data_list %>%
  mutate(
    fit = future_map(dataset,
                     ~ glm(genotype ~ avg_qual_mean + offset(iaf),
                           family ="binomial",
                           data=.x)),
    tidied = future_map(fit, tidy),
    glanced = future_map(fit, glance)
)
```

get all p-values

```{r}
p_values_dt <-
  data_list  %>% 
  select(tidied) %>% 
  map_depth( 2, "p.value") %>% 
  map_depth( 2, c(2)) %>% # c(1) for the intercept
  unlist(use.names = FALSE) %>% 
  enframe(name = "locus" ,
          value= "p.value")%>%
  mutate(locus= data_list$locus)

p_values_dt
```

```{r}
estimates_dt <-
  data_list  %>% 
  select(tidied) %>% 
  map_depth( 2, "estimate")%>% 
  map_depth( 2, c(2)) %>% # c(1) for the intercept
  unlist(use.names = FALSE) %>% 
  enframe(name = "locus" ,
          value= "beta_hat")%>%
  mutate(locus= data_list$locus)

estimates_dt
```
```{r}
ggplot(p_values_dt)+
  geom_histogram((aes(x=p.value)), bins=100) +
  theme_bw()
```

get a p-value for target specific loci
